CF Registry Analysis - ROC

### 2024-03-11 Christine Chan/CF Registry/cf_registry_ROC_analysis.qmd
CFRD registry rough draft

## Two hour OGTT value

### Full cohort

#### $\geq$ 200 vs. $<$ 200

```{r}
#| message: false
roc_df$CFRD <- as.numeric(roc_df$twohour_bloodglucose >= 200)
cfrd_roc <- roc(CFRD ~ hgba1c, data = roc_df)
thresh <- coords(cfrd_roc, "best", best.method = "youden")
plot(cfrd_roc, print.auc = T, print.thres = T)
gt(coords(cfrd_roc)) %>% fmt_number(decimals = 3)
```

#### $\geq$ 140 vs. $<$ 140

```{r}
#| message: false
roc_df$AGT <- as.numeric(roc_df$twohour_bloodglucose >= 140)
agt_roc <- roc(AGT ~ hgba1c, data = roc_df)
thresh <- coords(agt_roc, "best", best.method = "youden")
plot(agt_roc, print.auc = T, print.thres = T)
gt(coords(agt_roc)) %>% fmt_number(decimals = 3)
```

### Peds

```{r}
peds_df <- roc_df %>% filter(Age_YrEnd < 18)
```

#### $\geq$ 200 vs. $<$ 200

```{r}
#| message: false
peds_df$CFRD <- as.numeric(peds_df$twohour_bloodglucose >= 200)
cfrd_roc <- roc(CFRD ~ hgba1c, data = peds_df)
thresh <- coords(cfrd_roc, "best", best.method = "youden")
plot(cfrd_roc, print.auc = T, print.thres = T)
gt(coords(cfrd_roc)) %>% fmt_number(decimals = 3)
```

#### $\geq$ 140 vs. $<$ 140

```{r}
#| message: false
peds_df$AGT <- as.numeric(peds_df$twohour_bloodglucose >= 140)
agt_roc <- roc(AGT ~ hgba1c, data = peds_df)
thresh <- coords(agt_roc, "best", best.method = "youden")
plot(agt_roc, print.auc = T, print.thres = T)
gt(coords(agt_roc)) %>% fmt_number(decimals = 3)
```

@@

```{r}
adult_df <- roc_df %>% filter(Age_YrEnd >= 18)
```

#### $\geq$ 200 vs. $<$ 200

```{r}
#| message: false
adult_df$CFRD <- as.numeric(adult_df$twohour_bloodglucose >= 200)
cfrd_roc <- roc(CFRD ~ hgba1c, data = adult_df)
thresh <- coords(cfrd_roc, "best", best.method = "youden")
plot(cfrd_roc, print.auc = T, print.thres = T)
gt(coords(cfrd_roc)) %>% fmt_number(decimals = 3)
```

#### $\geq$ 140 vs. $<$ 140

```{r}
#| message: false
adult_df$AGT <- as.numeric(adult_df$twohour_bloodglucose >= 140)
agt_roc <- roc(AGT ~ hgba1c, data = adult_df)
thresh <- coords(agt_roc, "best", best.method = "youden")
plot(agt_roc, print.auc = T, print.thres = T)
gt(coords(agt_roc)) %>% fmt_number(decimals = 3)
```

>>>>

For the following analyses, we considered those with a two hour glucose value >= 140 and < 200 as a distinct group (AGT) and use receiver operating characteristic curves to find cutoffs that predict:

1. NGT vs. AGT

2. AGT vs. CFRD

```{r}
ngt_agt <- roc_df %>% filter(`OGTT 2-hour` != ">=200")
ngt_agt$ogtt <- droplevels(ngt_agt$`OGTT 2-hour`)
agt_cfrd <- roc_df %>% filter(`OGTT 2-hour` != "<140")
agt_cfrd$ogtt <- droplevels(agt_cfrd$`OGTT 2-hour`)
```

## Peds and adults

### NGT vs. AGT

```{r}
#| message: false
r <- roc(ogtt ~ hgba1c, data = ngt_agt)
thresh <- coords(r, "best", best.method = "youden")
plot(r, print.auc = T, print.thres = T)
gt(coords(r)) %>% fmt_number(decimals = 3)
summary(r)
```

#### AGT vs. CFRD

```{r}
#| message: false
r <- roc(ogtt ~ hgba1c, data = agt_cfrd)
thresh <- coords(r, "best", best.method = "youden")
plot(r, print.auc = T, print.thres = T)
gt(coords(r)) %>% fmt_number(decimals = 3)
summary(r)
```

## Peds

```{r}
peds_ngt_agt <- ngt_agt %>% filter(Age_YrEnd < 18)
peds_agt_cfrd <- agt_cfrd %>% filter(Age_YrEnd < 18)
```

### NGT vs. AGT

```{r}
#| message: false
r <- roc(ogtt ~ hgba1c, data = peds_ngt_agt)
thresh <- coords(r, "best", best.method = "youden")
plot(r, print.auc = T, print.thres = T)
gt(coords(r)) %>% fmt_number(decimals = 3)
summary(r)
```

#### AGT vs. CFRD

```{r}
#| message: false
r <- roc(ogtt ~ hgba1c, data = peds_agt_cfrd)
thresh <- coords(r, "best", best.method = "youden")
plot(r, print.auc = T, print.thres = T)
gt(coords(r)) %>% fmt_number(decimals = 3)
summary(r)
```

@@

```{r}
adult_ngt_agt <- ngt_agt %>% filter(Age_YrEnd >= 18)
adult_agt_cfrd <- agt_cfrd %>% filter(Age_YrEnd >= 18)
```

### NGT vs. AGT

```{r}
#| message: false
r <- roc(ogtt ~ hgba1c, data = adult_ngt_agt)
thresh <- coords(r, "best", best.method = "youden")
plot(r, print.auc = T, print.thres = T)
gt(coords(r)) %>% fmt_number(decimals = 3)
summary(r)
```

#### AGT vs. CFRD

```{r}
#| message: false
r <- roc(ogtt ~ hgba1c, data = adult_agt_cfrd)
thresh <- coords(r, "best", best.method = "youden")
plot(r, print.auc = T, print.thres = T)
gt(coords(r)) %>% fmt_number(decimals = 3)
summary(r)
```
